---
title       : Simple Web-based Asset Allocation Tool
subtitle    : 
author      : The Ultimate Learner
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Investing Matters!!

* Saving for the future involves a level of risk-taking
* Allocating money to different stocks can maximize return and minimize risk
* The big question is: How can an investor build the right portfolio to meet the two goals?

--- .class #id 

## The answer: 

* Go to this [site] (https://brainlessok.shinyapps.io/Project/)
* Enter up to 5 stock ticker symbols of your favourite companies or components of your current portfolio
* Click "Submit"
* If you have problem figuring out their stock symbol, click [here] (http://www.marketwatch.com/tools/quotes/lookup.asp?siteID=mktw&Lookup=Boeing&Country=us&Type=All). 

--- .class #id 

## Recent Returns
* The application will display the monthly return for each stock since January 2013
* For example: For Boeing, IBM, Johnson and Johnson, Proctor and Gamble, and Exxon Mobile
```{r echo=FALSE}
library("stockPortfolio")
x=c("BA","IBM","JNJ","PG","XOM")
get_returns_output=getReturns(x,freq="month",start='2013-1-1')

```
```{r echo=FALSE, results='asis'}
summary(get_returns_output)

```

--- .class #id 

## Optimal Portfolio Allocation for the Five
* The optimal allocation for the sample of 5 stocks are:  

1. Boeing:15.64%  
2. IBM:19.24%
3. JNJ:30.42%
4. PG:31.79%
5. XOM:2.91%

--- .class #id 

## References
* R package [stockPortfolio] (http://cran.r-project.org/web/packages/stockPortfolio/stockPortfolio.pdf) is used to build the simle web-based application.  
* Look it up and build your own allocation application!

